The Bug Catalog of the Maven Ecosystem

### 2014-01-19 docs/msr.tex
changed title, adding content in Section 2

\title{The Bug Catalog of the Maven Repository Ecosystem}

@@

\section{Data Collection Experiment}
\label{sec:exp}
Body.

@@

\section{Tools}
\label{sec:exp}
Tools.

@@

\section{Acknowledgments}
possible acks.

>>>>

\title{The Bug Catalog of the Maven Ecosystem}

@@

\section{Data Collection Experiment}
\label{sec:exp}

First, we scanned the Maven repository only
for appropriate {\sc jar}s and created a list that included them.
This is because FindBugs analyzes applications written in Java,
and the Maven repository hosts projects from
languages other than Java such as Scala, Groovy,
Clojure, etc. Thus we filtered out such projects.
In particular, we obtained a snapshot (January 2012) of
the repository and handled it locally to retrieve a list of all
the names of the project versions that existed in it.
A project version can be uniquely identified by the triplet:
{\it group id}, {\it artifact id} and {\it version}.

With the {\sc jar} list at hand, we created a series of processing tasks
and added them to the task queue. Then we executed twenty five (Unix-based)
workers that checked out tasks from the queue, processed the data and stored the
results to the data repository.

A typical processing cycle of a worker included the following steps: after
the worker spawned, it requested a task from the queue. This task contained
the {\sc jar} name, which was typically a project version that was downloaded locally.
First, specific {\sc jar} metadata were calculated and stored. Such metadata included
its size, its dependencies, and a number that represented the chronological order of the
release. This order was derived from an {\sc xml} file that
accompanies every project in the Maven repository called {\it
maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
also stored in the data repository. When the task was completed the queue
was notified and the next task was requested. This process was executed for
all the available {\sc jar}s in the task queue. A schematic representation of
the data processing architecture can be seen in Figure~\ref{fig:arch}.

\begin{figure}[t]
  \begin{center}
    \includegraphics[scale=0.73]{figures/arch.pdf}
  \end{center}
  \caption{The data processing architecture.}
  \label{fig:arch}
\end{figure}

@@

@@
